### 2021-02-03 README.Rmd
Add codecov

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/worcs?color=blue)](https://r-pkg.org/pkg/worcs)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
[![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

@@

By participating in this project, you agree to abide by the [Contributor
Code of Conduct v2.0](https://www.contributor-covenant.org/). Contributions to the package must adhere to the [tidyverse style guide](https://style.tidyverse.org/). When contributing code, please add tests for that contribution to the `tests/testthat` folder, and ensure that these tests pass on [Travis-CI](https://travis-ci.org/github/cjvanlissa/worcs).

>>>>

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/worcs?color=blue)](https://r-pkg.org/pkg/worcs)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R-CMD-check](https://github.com/cjvanlissa/worcs/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/worcs/actions)
[![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969)
[![test-coverage](https://github.com/cjvanlissa/worcs/workflows/test-coverage/badge.svg)](https://github.com/cjvanlissa/worcs/actions)
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

@@

By participating in this project, you agree to abide by the [Contributor
Code of Conduct v2.0](https://www.contributor-covenant.org/). Contributions to the package must adhere to the [tidyverse style guide](https://style.tidyverse.org/). When contributing code, please add tests for that contribution to the `tests/testthat` folder, and ensure that these tests pass in the [GitHub Actions panel](https://github.com/cjvanlissa/worcs/actions/workflows/R-CMD-check).
